### 2020-12-03 AISTATS2021_Author_Response_Pack/aistats2021_author_response.tex
update;

	\textbf{Response to R1.}

	\textbf{Response to R2.}

>>>>

	\textbf{Response to R1.} Please see our response to the detailed comments.
	\textbf{(8-i)} Yes, the variance decreases because $||{a_i^{\star}}||^2 \le 1$.
	The bias increases because the bias of single-task learning (the ordinary least squares solution) is zero when $n > p$.
	\textbf{(8-ii)} By lower order terms, we mean any term that vanishes to zero when $p$ increases to infinity.
	\textbf{(8-iii)} The sum of $||{a_i^{\star}}||^2$ is one (or $r$ in general), because $A^{\star}$ is a (subspace) projection matrix.
	\textbf{(8-iv)} %We want to point out that the problem setting in Section 3 is in general non-convex. Therefore, it is not possible to explicitly solve $A_1, A_2$ without making further assumptions.
	We can assume knowledge of $A_1 \in \mathbb R, A_2 \in \mathbb R$ without loss of generality since they can be solved numerically by using a subset of training data points (e.g. $\sqrt{p}$ suffices).
	The sampling error of the numerical solution is $O(\exp(-p))$.

	\textbf{Response to R2.} We thank the reviewer for providing detailed feedback.
	Response to questions under Section 8.
	\textbf{(i)}
	In the over-parametrized regime, the minimum solution of $f(A ,B)$ (equation 1) reduces to single-task learning.
	Hence, studing this regime is problematic without adding explicit regularization or implicit algorithmic biases.
	These are interesting research questions, but beyond the scope of our work.
	\textbf{(ii)}

	Response to questions under Section 3.
	\textbf{(1-i)}
